PragBat Analysis

### 2022-04-07 analysis/analysis.Rmd
prep merge

```{r}
model_cor <- data_frame()

tasks1 <- unique(data$task[data$study == "study1"])

for(i in tasks1) {

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study1", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 4000)

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study1")

          model_cor <- bind_rows(model_cor, cor)

}

tasks2 <- unique(data$task[data$study == "study2"])

for(i in tasks2) {

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study2", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 4000)

          cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_day1,test_day2)")%>%mutate(task = i , study = "study2")

          model_cor <- bind_rows(model_cor, cor)

}

mcor <- model_cor %>%
    mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"),
           term = task, 
           mcor = Estimate, 
           mcor_lci = `l-95% CI`, 
           mcor_uci = `u-95% CI`)%>%
  select(study, term, task, mcor, mcor_lci, mcor_uci)

saveRDS(mcor, "../saves/model_based_reliability.rds")

@@

```{r}
wide_data <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study != "study3",
         task != "training") %>%
  droplevels() %>%
  group_by(study,id,task, test_day) %>%
  summarise(mean = mean(correct)) %>%
  spread(test_day, mean) %>%
  na.omit() %>%
  rename("Day1" = `day1`,
         "Day2" = `day2`)

@@

cp1 <- ggplot(cor_r1, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor2), color = "black", size = 3) +
  #ggtitle("Study 1")+
  theme(
        legend.position = "right",
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

cp2 <- ggplot(cor_r2, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor2), color = "black", size = 3) +
  #ggtitle("Study 2")+
  theme(
        legend.position = "right",
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

cp3 <- ggplot(cor3, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 12)+
  #ggtitle("Study 3")+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(legend.justification = c(1, 0),
        legend.position = c(0.55, 0.75),
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.background = element_blank())+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))

pf4 <- ggarrange(cp1, cp2, cp3, common.legend = T, legend = "right", nrow = 1, labels = c("A","B","C"), hjust = -1.5)

ggsave(plot = pf4,"./figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
```

>>>>

```{r}
# model_cor <- data_frame()
# 
# tasks1 <- unique(data$task[data$study == "study1"])
# 
# for(i in tasks1) {
# 
#   model <- brm(correct ~  z_age + (0+test_day|id),
#             data = data%>%filter(study == "study1", task == i), 
#             family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           #save_all_pars = TRUE,
#           iter = 4000)
# 
#           cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study1")
#           
#           model_cor <- bind_rows(model_cor, cor)
#   
# }
# 
# tasks2 <- unique(data$task[data$study == "study2"])
# 
# for(i in tasks2) {
# 
#   model <- brm(correct ~  z_age + (0+test_day|id),
#             data = data%>%filter(study == "study2", task == i), 
#             family = bernoulli(),
#           #control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4,
#           cores = 4,
#           #save_all_pars = TRUE,
#           iter = 4000)
# 
#           cor <- summary(model)$random$id%>%as_tibble(rownames = "parameter")%>%filter(parameter == "cor(test_dayday1,test_dayday2)")%>%mutate(task = i , study = "study2")
#           
#           model_cor <- bind_rows(model_cor, cor)
#   
# }
# 
# 
# mcor <- model_cor %>%
#     mutate(task = recode(task,
#                     `mutual_exclusivity` = "Mutual Exclusivity",
#                     `informativeness` = "Informativeness Inference (1)",
#                     `simple_inf` = "Informativeness Inference (2)",
#                     `preference` = "Speaker Preference",
#                     `novelty` = "Discourse Novelty",
#                     `card_sorting` = "Card Sorting",
#                     `discourse_continuity` = "Discourse Continuity",
#                     `ad_hoc_implicature` = "Ad-hoc Implicature",
#                     `match_to_sample` = "Relational Match-to-sample"),
#            term = task, 
#            mcor = Estimate, 
#            mcor_lci = `l-95% CI`, 
#            mcor_uci = `u-95% CI`)%>%
#   select(study, term, task, mcor, mcor_lci, mcor_uci)
# 
# saveRDS(mcor, "../saves/model_based_reliability.rds")

@@

```{r}
wide_data <- data %>%
  mutate(task = recode(task,
                    `mutual_exclusivity` = "Mutual Exclusivity",
                    `informativeness` = "Informativeness Inference (1)",
                    `simple_inf` = "Informativeness Inference (2)",
                    `preference` = "Speaker Preference",
                    `novelty` = "Discourse Novelty",
                    `card_sorting` = "Card Sorting",
                    `discourse_continuity` = "Discourse Continuity",
                    `ad_hoc_implicature` = "Ad-hoc Implicature",
                    `match_to_sample` = "Relational Match-to-sample"))%>%
  filter(study != "study3",
         task != "training") %>%
  droplevels() %>%
  group_by(study,id,task, test_day) %>%
  summarise(mean = mean(correct)) %>%
  spread(test_day, mean) %>%
  na.omit() %>%
  rename("Day1" = `1`,
         "Day2" = `2`)

@@

cp1 <- ggplot(cor_r1, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="") +
   coord_fixed()+
  theme_few()+
  geom_text(aes(label = cor2), color = "black", size = 3) +
  #ggtitle("Study 1")+
  theme(legend.text=element_text(size=8),
        legend.background = element_blank(),
        legend.position = c(0.15, 0.75),
        legend.direction = "vertical",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

cp2 <- ggplot(cor_r2, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few()+
  guides(fill = "none")+
  geom_text(aes(label = cor2), color = "black", size = 3) +
  #ggtitle("Study 2")+
  theme(
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

cp3 <- ggplot(cor3, aes(x = term, y = task, fill = cor))+
  geom_tile(color = "white")+
  labs(x = "", y = "")+
  scale_fill_gradient2(low = "#CC6677", high = "#117733", mid = "white",
   midpoint = 0, limit = c(-1,1), space = "Lab",
   name="Correlation") +
   coord_fixed()+
  theme_few(base_size = 12)+
  guides(fill = "none")+
  #ggtitle("Study 3")+
  geom_text(aes(label = cor), color = "black", size = 3) +
  theme(
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

pf4 <- ggarrange(cp1, cp2, cp3, common.legend = F, nrow = 1, labels = c("A","B","C"), hjust = -1.5)

ggsave(plot = pf4,"../paper/figures/figure4.png", width = 10, height = 3, scale = 1.5, bg = "white")
```
